### 2023-01-14 code/plots.Rmd
fix selection of best escapement / msy action

```{r}
ppo <- read_csv("../data/PPO.csv")
```

```{r}
ppo |> 
  mutate(pop = (sp1+1)/2, 
         escapement = pop - action * pop) |> 
  ggplot(aes(t, escapement, group=rep)) + geom_line() + ylim(0,1)
```

```{r}
msy <- read_csv("../data/msy.csv")
best <- msy |> 
  filter(t == max(t)) |> 
  group_by(action) |> summarise(reward = mean(reward)) |> 
  filter(reward == max(reward))
best
```
```{r}
msy_sim <- msy |>
  filter(action == best$action) |> 
  pivot_longer(c("sp1", "sp2", "sp3"), names_to = "species", values_to = "abundance")

@@

```{r}
escapement <- read_csv("../data/escapement.csv.gz")
best_e <- escapement |> 
  filter(t == max(t)) |> 
  group_by(action) |> summarise(reward = mean(reward)) |> 
  filter(reward == max(reward))
best_e
```

```{r}
esc_sims <- escapement |>
  filter(action == best_e$action) |> 
  mutate(effort = pmax(1 - action / sp1, 0)) |>
  pivot_longer(c("sp1", "sp2", "sp3"), names_to = "species", values_to = "abundance")

esc_sims |>
  ggplot(aes(t, abundance, group = interaction(species, rep), col=species)) + geom_line(alpha=0.2)

esc_sims |> ggplot(aes(t,action, group=rep)) + geom_line(alpha=.2)

esc_sims |> ggplot(aes(t,effort, group=rep)) + geom_line(alpha=.2)
```

>>>>

# Constant Effort

```{r}
msy <- read_csv("../data/msy.csv.gz")
best <- msy |> 
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(reward = mean(reward)) |> 
  filter(reward == max(reward))
best
```

```{r}
msy_sim <- msy |>
  filter(action == best$action) |> 
  pivot_longer(c("sp1", "sp2", "sp3"), names_to = "species", values_to = "abundance")

@@

# Constant Escapement

```{r}
escapement <- read_csv("../data/escapement.csv.gz")

escapement |> 
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(reward = mean(reward)) |> 
  filter(reward == max(reward))

esc_sims <- escapement |> 
  filter(action == 0.58) |>
  rename(escapement = action) |>
  mutate(effort = pmax(1 - escapement / (sp1+1), 0))

esc_sims |> group_by(rep) |> filter(t == max(t)) |> pull(reward) |> mean()
```

```{r}
esc_sims |>
  pivot_longer(c("sp1", "sp2", "sp3"),
               names_to = "species", values_to = "abundance") |>
    filter(rep < 3) |>
  ggplot(aes(t, abundance, group = interaction(species, rep), col=species)) +
  geom_line(alpha=0.5) + facet_wrap(~rep, ncol=1)
```

```{r}
ppo |> 
  mutate(escapement = (sp1+1) - action * (sp1+1) -1,
         harvest = action - 1) |>
  pivot_longer(c("sp1", "sp2", "sp3", "escapement", "harvest"),
               names_to = "species", values_to = "abundance") |>
  ggplot(aes(t, abundance, col=species, group=interaction(rep, species))) +
  geom_line(alpha=0.6) + facet_wrap(~rep, ncol=1)

esc_sims |>

esc_sims |> ggplot(aes(t,action, group=rep)) + geom_line(alpha=.6)

esc_sims |> ggplot(aes(t,effort, group=rep)) + geom_line(alpha=.6)
```

# PPO Agent

```{r}
ppo <- read_csv("../data/PPO250.csv.gz")

```{r}
#ppo |> ggplot(aes(t, sp1, group=rep)) + geom_line()

ppo |> ggplot(aes(t, reward, group=rep)) + geom_line()

ppo |> 
  mutate(pop = (sp1+1), 
         escapement = pop - action * pop) |> 
  ggplot(aes(t)) +
  #geom_line(aes(t, pop, group=rep), col="black",alpha=0.1) +
  geom_line(aes(t, escapement, group=rep),  col="black",alpha=0.2)

ppo |> 
  mutate(escapement = (sp1+1) - action * (sp1+1) -1,
         harvest = action - 1) |>
  pivot_longer(c("sp1", "sp2", "sp3", "escapement", "harvest"),
               names_to = "species", values_to = "abundance") |>
  group_by(t,species) |>
  summarise(abundance = mean(abundance)+1) |>
  ggplot(aes(t, abundance, col=species)) +
  geom_line(alpha=0.6)

```{r}
ppo |> 
  mutate(escapement = (sp1+1) - action * (sp1+1) -1,
         harvest = action - 1) |>
  pivot_longer(c("sp1", "sp2", "sp3", "escapement", "harvest"),
               names_to = "species", values_to = "abundance") |>
  filter(rep < 3) |>
  ggplot(aes(t, abundance, col=species, group=interaction(rep, species))) +
  geom_line(alpha=0.6) + facet_wrap(~rep, ncol=1)
```

```{r}
ppo |> filter(t == max(t)) |> pull(reward) |> mean()

ppo |> filter(t == max(t)) |> pull(reward) |> sd()
